### 2018-04-15 ident/docs/sifigures.tex
most likely has all needed si figures

>>>>

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight, keepaspectratio]{figures/figure4/v3_1_2_data_utility}}
	\caption{Utility of data from combinations of two different experiments for identifying two parameters in $v_3$ when a) $K_3^{pep}$ is held constant, and when b) $K_3^{fdp}$ is held constant. Notice that a significant number of combinations can identify both $V_3^{max}$ and $K_3^{pep}$ when $K_3^{fdp}$ is known and fixed.}%\label{fig:figure2}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/figure2/v1_k1cat_exp_info}}
	\caption{Contribution of different experiment types towards identification of a) $k_1^{cat}$ and b) $K_1^{ac}$ in $v_1$ based on using data from two different experiments. Data from MWC model.}%\label{fig:figure2}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight, keepaspectratio]{figures/figure2/v1_V1max_v2_v5_2_ck_exp_info}}
	\caption{The contribution of different experiments types used in a combination of two experiments ($j = \{1, 2\}$) that can practically identify parameter a) $V_e^{max}$ and b) $K_e^{fdp}$ in $v_5$. Since $V_e^{max}$ is globally identifiable, it has a unique root. Since $K_e^{fdp}$ has two roots, is locally identifiable. However, results for the only practically identifiable root, based on the physical relevance constraints used in the analysis, is shown. Data from Convenience kinetics model is used.}%\label{fig:v5_exp_info}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=1.0\textheight, keepaspectratio]{figures/figure2/v3_1_2_exp_info}}
	\caption{The contribution of different experiments types used in a combination of three experiments ($j = \{1, 2, 3\}$) that can practically identify parameter a) $V_3^{max}(1)$, b) $K_3^{fdp}(1)$, c) $K_3^{pep}(1)$, d) $V_3^{max}(2)$, e) $K_3^{fdp}(2)$ and f) $K_3^{pep}(2)$ for $v_3$. parameters $V_3^{max}$, $K_3^{fdp}$, and $K_3^{pep}$ are locally identifiable and have two possible roots. The first set of roots are designated as $V_3^{max}(1)$, $K_3^{fdp}(1)$ and $K_3^{pep}(1)$, and the second set of roots are designated as $V_3^{max}(2)$, $K_3^{fdp}(2)$ and $K_3^{pep}(2)$. The percentages reflect the fractional contribution of each experiment type towards all identifiable data combinations. The contribution of the five different experiment types towards identifiability of either of the two roots for each of the three parameters is the same.}\label{fig:v3_exp_info}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.6\textheight, keepaspectratio]{figures/figure2/v3_var_1_2_exp_info}}
	\caption{Contribution of different types of experiments for using data from two different experiments towards identification of a) $V_3^{max}$ and b) $K_3^{fdp}$ in $v_3$ when $K_3^{pep}$ is held constant, and c) $V_3^{max}$ and d) $K_3^{pep}$ when $K_3^{fdp}$ is held constant.}%\label{fig:figure2}
\end{figure}

\begin{figure}[!tbhp]
	\centering{\includegraphics[width=1.0\textwidth,height=0.3\textheight, keepaspectratio]{figures/figure6/v1_v1max_k1cat_parameter_value}}
	\caption{Distribution of identified/estimated parameter values for flux $v_1$ from different experimental data combinations. The box plot of the estimated values of $V_1^{max}$ and $K_1^{ac}(ne)$ are juxtaposed with the box plots of the calculated values of $k_1^{cat}$ based on the estimated value of $V_1^{max}$ and the enzyme concentrations available from the two different experiments used to estimate $V_1^{max}$ and $K_1^{ac}(ne)$}\label{fig:parameter_value_v1_v1max_kcat}
\end{figure}
